\section{Future Work}
\label{sec:future}


%% Say we should explore other representations and optimizations

There are other optimizations to OBDDs that we have not explored in
this paper. For example, adding negated edges to OBDDs can result in
smaller structures for some Boolean functions.\footnote{Following
a negated edge in an OBDD flips the value of the result.} Incorporating these
optimizations in our protocol while preserving privacy is a direction
for future work. There are several other OBDD-like representations
developed by the computer-aided design and computer aided
verification research communities, such as Binary Moment Diagrams
(BMDs)~\cite{BMD} and  Hybrid Decision Diagrams (HDDs)~\cite{HDD}. For a
certain class of functions, these representations are more succinct
than OBDDs. For example, BMDs can efficiently represent integer
multiplication, which cannot be represented efficiently at the
bit-level with OBDDs. Extending our protocol for these representations
is an important direction of future research. Our vision is to provide
an option for all these representations in our system so that a user can
choose the representation that is suitable for the problem.

%% Applications

OBDDs have been used for a variety of applications, such
efficient filtering in publish-subscribe systems~\cite{Jha:ICSE},
program analysis~\cite{Whaley}, and planning~\cite{Jensen}. In the future we
will investigate whether our protocol can be extended to design
privacy-preserving algorithms for these applications.
